When are Fuzzy Extractors Possible?

### 2014-10-06 info-bounds/FuzzyExtPossibility.tex
minor last minute edits

\bnote{mention secure sketches?}
\bnote{keep editing}
\bnote{nearby or close?  be consistent}
\bnote{I renamed section titles to get rid of distribution aware and oblivious.  don't quite like them}
\lnote{mention computational setting?}
\lnote{mention the typical analysis that separates min-entropy and error-tolerance?}
\end{abstract}

@@

\subsection{Fuzzy min-entropy: a Necessary Condition}
\label{sec:minimal conditions}
The value $p$ allows everyone, including the adversary, to find the output of $\rep(\cdot, p)$ on any input $w'$. Ideally,  $p$ should not provide any useful information beyond this ability, and the outputs of $\rep$ on inputs that are too distant from $w$ should provide no useful information, either.  In this ideal scenario, the adversary is limited to trying to guess a $w'$ that is $t$-close to $w$. 
Letting $w'$ be the center of the maximum-weight ball in $W$ would be optimal for the adversary.
We therefore measure the quality of a source by (the negative logarithm of) this weight.

@@

\begin{definition}
Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{known distribution secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness:} 
$
\forall w\in W$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
Correctness is guaranteed only for the support of $W$.
\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.  We assume known distribution algorithms are \emph{inefficient}.  Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.

@@

\subsection{Flat distributions}
A distribution is flat if all points in its support have the same probability. Let $\supp(W)$ denote the support of $W$< i.e., the set of points with nonzero probability.
\begin{definition}
A distribution $W$ is \emph{flat} if for all $w_0, w_1 \in \supp(W)$,  $\Pr[W=w_0] = \Pr[W=w_1]$.  
\end{definition}

Denote the ball of radius $t$ with the largest number of points in the support of $W$ as $B_{t, max}$.   For flat distributions, the weight of this maximum-probability ball (which determines $\Hfuzz(W)$ by \defref{def:fuzzy min-ent}) is proportional to the number of points in it.  More precisely, 
\begin{align}
\Hfuzz(W) &= -\log \left(\max_{w' \in \mathcal{M}} \left| \{w | w\in \supp(W) \wedge \dis(w, w')\le t\} \right|\cdot \Pr[W=w]\right) \nonumber \\
&= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in \supp(W) \wedge \dis(w, w')\le t\}| \cdot 2^{-\Hoo(W)}\right) \nonumber \\
&=\Hoo(W) -\log\left( \max_{w' \in \mathcal{M}}| \{w | w\in \supp(W) \wedge \dis(w, w')\le t\} |\right)\nonumber \\
&= \Hoo(W) -\log |B_{t, max}\cap \supp(W)|.\label{eq:fuzz for flat}
\end{align}

@@

\begin{lemma}
\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{|B_{t, max}|-1}{|R|}$. 
\end{lemma}
\begin{corollary}
Let $n = \log |\mathcal{M}|$.  If $|R| \ge |B_{t, max}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |B_{t, max}\cap\supp(W)| + \omega(\log n)$ suffices.
\end{corollary}

\noindent
\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is 
$
\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t, max}\cap\supp(W)| - \omega(\log n).
$
For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.

@@

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$. Let $W$ be a distribution with $\Hoo(W)= m$.  Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., m+\ell$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions.  Define $\sketch_W, \rec_W$ as: 
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item If $\Pr[W=w] \le 2^{-(m+\ell)}$. Set $p=0,w$.
\item Else
\begin{enumerate}
\item Find $i$ such that $\Pr[W=w]\in L_i$.
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $ss =1,  i, F_i(K, w), K$.
\end{enumerate}
\end{enumerate}
\vspace{.4in}
\end{minipage} &
\begin{minipage}{3.5in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', ss)$
\item If $ss_0 = 1$, output $ss_{1,..., |y|}$.
\item Else
\begin{enumerate}
\item Parse $(i, y, K) = ss_{1,..., |y|}$.
\item $W^* = \{w \in \supp(W) | \dis(w, w')\le t\}$.
\item For $w^*\in W^*$, if $F(K, w^*) = z$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

\noindent
We extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w' \in \mathcal{M}} \{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}.
\]

\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$ where $n =\log \M$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.  When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.

@@

\noindent
In our positive results we considered an arbitrary finite metric space.  The relevant parameters were the size of balls and the size of the metric space.  Our negative results are specific to the Hamming metric.
\section{Impossibility of Secure Sketches for all Families with $\Hfuzz$}
\label{sec:family of dist}

@@

Let $V$ be the process of uniformly sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.  Let the random variable $Z$ specify which $W$ was sampled.  The view of the challenger is $V$, while the view of the adversary is a distribution $V|Z$.  Our results rule out security for an average member of $\mathcal{W}$.  It may be possible to improve parameters by ruling out only a worst case $W$.  In \apref{sec:def equiv}, we show that providing security for a family $\mathcal{W}$ is equivalent to providing security for all distributions over that family.

@@

Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$, and let $Z$ specify which $W$ is sampled.  Then
\[
\Hav(V|\sketch(V), Z)< 2.
\]
\end{theorem}

@@

\begin{itemize}
\item \propref{prop:each element good}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.  Here we show the minimum distance of $V|\sketch(V)$ is at least $t$.
\item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 2$.
\end{itemize}
\end{proof}
\noindent
\textbf{Note:} There is a tradeoff between the size of $\mathbb{F}$ and the error tolerance required for the counter example.  By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.
\subsection{Implications for Computational Secure Sketches}
\label{sec:feas comp sec sketch}
Fuller et al. showed that computational secure sketches that provide pseudoentropy imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definition of Fuller et al. uses a weak version of pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.

@@

Secure sketches that provide computational unpredictability are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.  Our impossibility result says nothing about this weaker form of a secure sketch.  Extracting from unpredictability requires a extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.

\section{Impossibility of Fuzzy Extractors for all Families with $\Hfuzz$}
\label{sec:imposs fuzz ext}
In the previous section, we showed a family of distributions that does not admit a secure sketch.  We provide a similar result for fuzzy extractors.

\begin{theorem}
\label{thm:imposs fuzz ext}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{W}$ over $\zo^n$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$.  Let $\kappa \ge 2$, $t = \omega(n^{1/2}\log n)$.  Any $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$ has $\epsilon > 1/8 - \ngl(n)$.

Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$ and let $Z$ be the description of which $W$ is sampled.  Let $(\Key, P)\leftarrow \gen(V)$.  Then, 
\[
\sd ((\Key,P, Z), (U_\kappa, P, Z))>1/8-\ngl(n).
\]

@@

Our counterexample uses a slightly different family of distributions $\mathcal{W}$ than the counterexample for secure sketches.  
We can't work directly on the Hamming distance over a large alphabet~(as we did for secure sketches).  We embed this larger space to the binary Hamming metric.
Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} .
\]
The multiplication is in $\mathbb{F}$.
Define a distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
Let $\mathcal{W}$ be the set of all such $W$.

 Define $V$ as the process of uniformly choosing $W\leftarrow \mathcal{W}$ and then sampling from $w\leftarrow W$.  The adversary sees $\sketch(V)$ and which distribution was sampled, call this information $Z$. $Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/\nu}$.

@@

We now argue correctness.  Fix some $w, w'$.  Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$.  The size of $W^*$ is at most $B_{t, max}$.  Since $w, w'$ are independent of $\sketch$ this set is independent of the choice of $\mathcal{K}$.  The algorithm  $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ collides is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{|B_{t, max}|-1}{|R|}
\end{align*}
The inequality proceeds by union bound. The first equality proceeds by the universality of $F$ and the second inequality proceeds by noting the number of wrong neighbors is bounded by $|B_{t, max}|-1$.  This completes the proof.
\end{proof}

@@

Let $W^*$ denote the set of elements of $W$ in $L_i$ within distance $t$ of $w'$.  The size of $W^*$ is at most $B_{t, i, max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  The probability that another element $w^*$ matches the hash is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t, i, max}\cap \supp(W)|-1}{|R_i|} = \delta
\end{align*}
The inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $|B_{t, i, max}|$.

>>>>

\lnote{mention computational setting?}
\lnote{mention the typical analysis that separates min-entropy and error-tolerance?}

\medskip
\textbf{Keywords:} Fuzzy extractors, secure sketches, information theory, biometric authentication, error-tolerance, key derivation, error-correcting codes.
\end{abstract}

@@

\subsection{Fuzzy Min-Entropy: a Necessary Condition}
\label{sec:minimal conditions}
The value $p$ allows everyone, including the adversary, to find the output of $\rep(\cdot, p)$ on any input $w'$. Ideally,  $p$ should not provide any useful information beyond this ability, and the outputs of $\rep$ on inputs that are too distant from $w$ should provide no useful information, either.  In this ideal scenario, the adversary is limited to trying to guess a $w'$ that is $t$-close to $w$. 
Letting $w'$ be the center of the maximum-weight ball in $W$ would be optimal for the adversary.
We therefore measure the quality of a source by (the negative logarithm of) this weight.

@@

\begin{definition}
Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{known distribution secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness:} 
$
\forall w\in \supp(W)$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
Correctness is guaranteed only for the support of $W$.
\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.  We assume known distribution algorithms are \emph{inefficient}.  Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.

@@

\subsection{Flat Distributions}
A distribution is flat if all points in its support have the same probability. Let $\supp(W)$ denote the support of $W$, i.e., the set of points with nonzero probability.
\begin{definition}
A distribution $W$ is \emph{flat} if for all $w_0, w_1 \in \supp(W)$,  $\Pr[W=w_0] = \Pr[W=w_1]$.  
\end{definition}

Denote the ball of radius $t$ with the largest number of points in the support of $W$ as $B_{t,W,max} = \max_{w'\in\M} |\{w | w\in \supp(W) \wedge \dis(w ,w')\le t\}|$.   For flat distributions, the weight of this maximum-probability ball (which determines $\Hfuzz(W)$ by \defref{def:fuzzy min-ent}) is proportional to the number of points in it.  More precisely, 
\begin{align}
\Hfuzz(W) &= -\log \left(\max_{w' \in \mathcal{M}} \left| \{w | w\in \supp(W) \wedge \dis(w, w')\le t\} \right|\cdot \Pr[W=w]\right) \nonumber \\
&= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in \supp(W) \wedge \dis(w, w')\le t\}| \cdot 2^{-\Hoo(W)}\right) \nonumber \\
&= \Hoo(W) -\log |B_{t,W,max}|.\label{eq:fuzz for flat}
\end{align}

@@

\begin{lemma}
\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{|B_{t,W,max}|-1}{|R|}$. 
\end{lemma}
\begin{corollary}
Let $n = \log |\mathcal{M}|$.  If $|R| \ge |B_{t,W,max}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |B_{t,W,max}| + \omega(\log n)$ suffices.
\end{corollary}

\noindent
\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is 
$
\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t,W,max}| - \omega(\log n).
$
For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.

@@

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$. Let $W$ be a distribution with $\Hoo(W)= m$.  Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., m+\ell$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions.  Define $\sketch_W, \rec_W$ as: 
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item If $\Pr[W=w] \le 2^{-(m+\ell)}$. Set $p=0,w$.
\item Else
\begin{enumerate}
\item Find $i$ such that $\Pr[W=w]\in L_i$.
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $ss =1,  i, F_i(K, w), K$.
\end{enumerate}
\end{enumerate}
\vspace{.4in}
\end{minipage} &
\begin{minipage}{3.5in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', ss)$
\item If $ss_0 = 1$, output $ss_{1,..., |y|}$.
\item Else
\begin{enumerate}
\item Parse $(i, y, K) = ss_{1,..., |y|}$.
\item $W^* = \{w \in \supp(W) | \dis(w, w')\le t \\\, \, \, \wedge \Pr[W=w]\in L_i\}$.
\item For $w^*\in W^*$, if $F_i(K, w^*) = z$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

\noindent
We extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t,i,W, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t,W_i,max} = \max_{w' \in \mathcal{M}} \{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}.
\]

\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$ where $n =\log \M$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t,W_i,max}|-1) /\delta$.  When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.

@@

\noindent
In our positive results we considered an arbitrary finite metric space.  The relevant parameters were the size of balls and the size of the metric space.  Our negative results are specific to the Hamming metric.
\section{Impossibility of Secure Sketches for a Family with $\Hfuzz$}
\label{sec:family of dist}

@@

Let $V$ be the process of uniformly sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.  Let the random variable $Z$ indicate which $W$ was sampled.  The view of the challenger is $V$, while the view of the adversary is a distribution $V|Z$.  Our results rule out security for an average member of $\mathcal{W}$.  It may be possible to improve parameters by ruling out only a worst case $W$.  In \apref{sec:def equiv}, we show that providing security for a family $\mathcal{W}$ is equivalent to providing security for all distributions over that family.

@@

Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$, and let $Z$ indicate which $W$ is sampled.  Then
\[
\Hav(V|\sketch(V), Z)< 2.
\]
\end{theorem}

@@

\begin{itemize}
\item \propref{prop:each element good}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.  Here we show the minimum distance of $V|\sketch(V)$ is at least $t$.
\item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 2$.
\end{itemize}
\end{proof}
\noindent
\textbf{Note:} There is a tradeoff between the size of $\mathbb{F}$ and the error tolerance required for the counter example.  By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.\bnote{it would be nice to say what our counter example says about the binary space.}
\subsection{Implications for Computational Secure Sketches}
\label{sec:feas comp sec sketch}
Fuller et al. showed that computational secure sketches that provide pseudoentropy imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definition of Fuller et al. uses a weak version of pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.

@@

Secure sketches that provide computational unpredictability are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.  Our impossibility result says nothing about this weaker form of a secure sketch.  Extraction from unpredictability entropy can be done using an extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}; however, in the computational setting, the obfuscated function can simply hide a randomly generated key, and therefore extraction is not necessary to obtain a fuzzy extractor.

\section{Impossibility of Fuzzy Extractors for a Family with $\Hfuzz$}
\label{sec:imposs fuzz ext}
In the previous section, we showed a family of distributions that does not admit a secure sketch.  We provide a similar result for fuzzy extractors.

\begin{theorem}
\label{thm:imposs fuzz ext}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{W}$ over $\zo^n$ satisfying the following conditions. For each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$. Let $\kappa \ge 2$ and $t = \omega(n^{1/2}\log n)$.  Any $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$ has $\epsilon > 1/8 - \ngl(n)$.

Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$ and let $Z$ indicate which $W$ is sampled.  Let $(\Key, P)\leftarrow \gen(V)$.  Then, 
\[
\sd ((\Key,P, Z), (U_\kappa, P, Z))>1/8-\ngl(n)\,.
\]

@@

Our counterexample uses a slightly different family of distributions $\mathcal{W}$ than the counterexample for secure sketches.  
We will work over a binary alphabet~(we used a large alphabet in our counterexample for secure sketches).  In the binary Hamming space a large fraction of any set of bounded size is the near ``boundary'' of that set.  This will be important for our proof.  We will embed the larger alphabet we used into the binary Hamming metric.
Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} .
\]
The multiplication is in $\mathbb{F}$.
Define a distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
Let $\mathcal{W}$ be the set of all such $W$.

 Define $V$ as the process of uniformly choosing $W\leftarrow \mathcal{W}$ and then sampling from $w\leftarrow W$.  The adversary sees $\sketch(V)$  and $Z$, where $Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/\nu}$.

@@

We now argue correctness.  Fix some $w, w'$.  Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$.  The size of $W^*$ is at most $B_{t,W,max}$.  Since $w, w'$ are independent of $\sketch$ this set is independent of the choice of $\mathcal{K}$.  The algorithm  $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ collides is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{|B_{t,W,max}|-1}{|R|}
\end{align*}
The inequality proceeds by union bound. The first equality proceeds by the universality of $F$ and the second inequality proceeds by noting the number of wrong neighbors is bounded by $|B_{t,W,max}|-1$.  This completes the proof.
\end{proof}

@@

Let $W^*$ denote the set of elements of $W$ in $L_i$ within distance $t$ of $w'$.  The size of $W^*$ is at most $B_{t,W_i,max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  The probability that another element $w^*$ matches the hash is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t,W_i,max}|-1}{|R_i|} = \delta
\end{align*}
The inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $|B_{t,W_i,max}|$.
